---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# summaryandboxplot

<!-- badges: start -->
<!-- badges: end -->

The goal of summaryandboxplot is to summarize a numeric vector with summary stats (number of elements, number of unique elements, min, 1st quartile, median, mean, 3rd quartile, max, and number of NAs) and provide a box-and-jitter plot to produce a visual respresentation of the numeric vector.

## Installation

You can install the development version of summaryandboxplot like so:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-jowong4", ref = "0.1.0")
```

## Example

This is a basic example which shows you how to use summary_and_boxplot to summarize a numeric vector:

```{r example}
library(summaryandboxplot)

summary_and_boxplot(1:10)

summary_and_boxplot(c(1, 2, 3, 4, 5))
```


